\documentclass[a4paper,10pt]{article}

% Page geometry
\usepackage[margin=1.2cm]{geometry}

% Section formatting
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0pt}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0pt}{}
\titlespacing*{\section}{0pt}{8pt}{4pt}
\titlespacing*{\subsection}{0pt}{6pt}{3pt}

% Spacing and typography
\usepackage{parskip}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

% Colors
\usepackage{xcolor}

% Dark mode support (pass -jobname=cv-dark and \def\darkmode{} via CLI)
\newif\ifdarkmode
\ifdefined\darkmode\darkmodetrue\fi
\ifdarkmode
  \definecolor{bg}{HTML}{121416}
  \definecolor{fg}{HTML}{e0e0e0}
  \definecolor{accent}{HTML}{8cc5cf}
  \definecolor{rule}{HTML}{4f5663}
\else
  \definecolor{bg}{HTML}{ffffff}
  \definecolor{fg}{HTML}{000000}
  \definecolor{accent}{HTML}{0645AD}
  \definecolor{rule}{HTML}{000000}
\fi

% Icons + links
\usepackage[colorlinks=true, urlcolor=accent, linkcolor=accent]{hyperref}
\usepackage{fontawesome5}

% Allow slightly looser line breaking to avoid overfull hboxes
\tolerance=400
\emergencystretch=2em

% List styling
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}

% Horizontal rule under sections
\newcommand{\mysectionrule}{\vspace{-4pt}\noindent{\color{rule}\rule{\linewidth}{0.5pt}}\par\vspace{4pt}}

\pagenumbering{gobble}

\begin{document}
\pagecolor{bg}
\color{fg}

% ============================================================
% HEADER
% ============================================================
\begin{center}
    {\LARGE \textbf{Andr\'{e} A. Nogueira}} \\[2pt]
    {\large Senior Platform Engineer} \\[4pt]
    \faIcon{map-marker-alt} Lisbon, Portugal \quad
    \faIcon{envelope} \href{mailto:andre@techquests.dev}{andre@techquests.dev} \quad
    \faIcon{globe} \href{https://techquests.dev}{techquests.dev} \quad
    \faIcon{github} \href{https://github.com/aanogueira}{github.com/aanogueira} \quad
    \faIcon{linkedin} \href{https://linkedin.com/in/andre-a-nogueira}{LinkedIn}
\end{center}

% ============================================================
% SUMMARY
% ============================================================
\section*{Summary}
\mysectionrule
Platform engineering leader with 6+ years of experience building developer-centric infrastructure at scale,
specializing in internal developer platforms, cloud infrastructure (GCP, AWS, Azure), and DevSecOps.

\begin{itemize}
  \item \textbf{Scale:} Managing 1000+ Kubernetes clusters and enabling self-service infrastructure for 500+ engineers.
  \item \textbf{Developer Velocity:} Automated end-to-end onboarding/offboarding from days to 30 minutes (99\% reduction).
  \item \textbf{Platform Tooling:} Built a cloud abstraction platform, infrastructure oversight system, and permission escalation tool --- all with monitoring, alerting, and audit trails.
  \item \textbf{OSS \& Community:} Upstream Terraform GCP contributions, technical blog at techquests.dev, author company-wide internal courses.
\end{itemize}

% ============================================================
% EXPERIENCE
% ============================================================
\section*{Professional Experience}
\mysectionrule

\subsection*{Mollie}
\textit{Leading European payment service provider.} \\
\textbf{Senior Platform Engineer} \hfill Jan 2025 -- Present \\
\textbf{Platform Engineer II} \hfill Jan 2024 -- Dec 2024 \\
\textbf{Platform Engineer I} \hfill May 2023 -- Dec 2023

\smallskip
Promoted twice in under 2 years. Key contributions:

\begin{itemize}
  \item \textbf{Cloud Abstraction Platform:} Architected and maintained the company's internal cloud platform, managing 1000+ Kubernetes clusters and enabling self-service infrastructure provisioning for 500+ engineers, with Backstage-powered self-service interfaces.
  \item \textbf{Infrastructure Oversight System:} Designed a 3-component system (data collector $\rightarrow$ policy analyzer via OPA/Rego $\rightarrow$ automated action engine) providing real-time visibility and automated remediation across all infrastructure, with full observability.
  \item \textbf{Permission Escalation \& Security Hardening:} Built an audited, SOC2-compliant system enabling temporary cross-system privilege escalation with full audit trails; investigated and hardened broader infrastructure for SOC2 compliance.
  \item \textbf{Project Lifecycle Automation:} End-to-end onboarding/offboarding (IAM $\rightarrow$ cluster provisioning $\rightarrow$ CI/CD $\rightarrow$ project scaffolding), reducing setup from days to 30 minutes.
  \item \textbf{Certificate Management:} Full lifecycle certificate management solution with automated rotation and alerting.
  \item \textbf{Service Mesh:} Implemented service-to-service mTLS via Envoy across all production workflows.
  \item \textbf{Infrastructure as Code:} Authored reusable Terraform modules; contributed mTLS support to the upstream GCP Terraform provider and GCP Autoneg.
  \item \textbf{Technical Leadership:} Author company-wide courses on the internal cloud platform and Kubernetes; active on-call rotation; mentor within 9-person platform team.
\end{itemize}

\subsection*{SteelEye --- Site Reliability Engineer \hfill Oct 2021 -- May 2023}
\begin{itemize}
  \item Designed and built end-to-end infrastructure for a fintech startup across AWS and Azure; implemented data pipelines (Airflow, Prefect), Kafka, and Elasticsearch.
  \item Traveled on-site to banking clients (including UBS) for integration work under strict privacy constraints; drove SOC2, GDPR, and industry compliance certifications.
  \item Built CI/CD with GitHub Actions; deployed ELK and LGTM stacks for observability; managed certificate lifecycle and on-call.
  \item Co-led a distributed team of 6 (3 EU + 3 India) with engineering manager, owning system design and platform architecture.
\end{itemize}

\subsection*{Truphone (via Smart Consulting) --- DevSecOps Engineer \hfill Oct 2020 -- Sep 2021}
\begin{itemize}
  \item Architected an internal developer platform on AWS (EKS) for a 7-person team serving 300--400 engineers across \textasciitilde{}300 Kubernetes clusters, accelerating service bootstrapping and integration.
  \item Implemented full lifecycle security controls: code scanning (SonarQube), custom CI runners/controllers, image scanning, and audit trails via GitLab CI.
  \item Managed self-hosted Kafka and Spark clusters, Elasticsearch, API gateway configurations, and Keycloak identity provider.
  \item Led a sub-team of 3 developers; built Go and TypeScript platform tooling; coordinated design and implementation of platform features.
\end{itemize}

\subsection*{La Redoute (via KCS IT) --- DevOps Engineer \hfill Sep 2019 -- Oct 2020}
\begin{itemize}
  \item Joined a newly formed cloud team (7 engineers) to migrate the company's entire on-prem infrastructure to GCP for 500+ engineers; managed 700+ Linux/Windows servers and legacy Puppet configurations.
  \item Built CI/CD platform from scratch (Jenkins, GitLab CI) with custom runners; authored Terraform modules for all infrastructure, permissions, and service provisioning.
  \item Self-hosted Kafka clusters, databases, and Kubernetes; created Helm charts and adapted Java workloads for cloud-native deployment.
  \item Deployed LGTM stack and Nagios for observability; implemented Vault for secrets management; built recovery automation tooling in Go, Python, and Bash.
\end{itemize}

% ============================================================
% PROJECTS
% ============================================================
\section*{Key Projects}
\mysectionrule
\textit{Details at \href{https://techquests.dev}{techquests.dev}}

\begin{itemize}
  \item \textbf{Code Search} --- Self-hosted platform for searching across repositories with bulk find-and-replace and automated PR creation (Go, Next.js, Zoekt, PostgreSQL)
  \item \textbf{houndr} --- Trigram-based code search engine with sub-millisecond search and zero-copy mmap indexing (Rust, Axum, libgit2)
  \item \textbf{git-context} --- CLI to switch between multiple Git identities and configurations; 93\%+ test coverage (Go)
  \item \textbf{howto} --- AI-powered shell command assistant supporting OpenAI, Anthropic, Gemini, DeepSeek (Go)
  \item \textbf{crontab-guru} --- TUI for creating/validating cron expressions with real-time feedback (Go, Bubble Tea)
  \item \textbf{HashPad} --- Zero-knowledge encrypted notepad stored entirely in URL hash, no backend (Vanilla JS, Web Crypto API)
  \item \textbf{Bip Bip} --- Co-founded logistics startup; incubated at Startup Leiria (SWOT, viability assessments, pitch decks); built initial demo and demand-matching algorithms; won mobility category prize at Startup Lisboa (Jul 2019 -- Jan 2025)
\end{itemize}

% ============================================================
% EDUCATION
% ============================================================
\section*{Education}
\mysectionrule

\textbf{Postgraduate Coursework in Cybersecurity and Forensic Informatics} \hfill 2019 -- 2020 \\
Polytechnic of Leiria \textit{(completed all coursework; thesis not pursued)}

\textbf{Bachelor's in Computer Science} \hfill 2015 -- 2019 \\
Polytechnic of Leiria

% ============================================================
% SKILLS
% ============================================================
\section*{Technical Skills}
\mysectionrule
\begin{itemize}
  \item \textbf{Programming:} Go, Rust, TypeScript, Python, C, Bash
  \item \textbf{Infrastructure:} Kubernetes, Terraform, ArgoCD, GitOps, Helm, Docker, Envoy, Backstage
  \item \textbf{Cloud:} GCP, AWS, Azure
  \item \textbf{Observability:} Prometheus, Grafana, Loki, Tempo, Mimir, Datadog, OpenTelemetry
  \item \textbf{Data \& Messaging:} PostgreSQL, Redis, Kafka, RabbitMQ, GCP Pub/Sub, Elasticsearch, Spark
  \item \textbf{Security:} Vault, SOPS, Trivy, SonarQube, mTLS, SOC2, OPA/Rego
  \item \textbf{Other:} CI/CD (GitHub Actions, GitLab CI, Jenkins), Linux
  \item \textbf{Languages:} Portuguese (Native), English (Fluent)
\end{itemize}

\end{document}
